scoring

### 2022-04-14 darts/scoring.Rmd
group over models and inter

```{r}
data <- read_csv("forecasts/block_rnn_stochastic_10.csv.gz")[-1]
emp_draws <- data %>% filter(true_model==TRUE) %>% select(-true_model)
forecasts <- data %>% filter(true_model==FALSE) %>% select(-true_model)
```

@@

## Currently it looks like only one tp_model and one ml_model, but 5 iterations:
## We will need to generalize this code to map over multiple tp_models and ml_models etc
# forecasts %>% count(tp_model, ml_model, iter)

## pivot forecast into a matrix of size(time) x size(ensembles)
i <- 1
dat <- forecasts |> filter(iter == i) |>
  select(t = time, i = ensemble, N = value) |> 
 pivot_wider(id_cols = "t", names_from="i", values_from = "N") |> 
  select(-t) |> as.matrix()

test <- emp_draws |> filter(iter == i)  |>
  select(t = time, i = ensemble, N = value)
```

```{r}
bench::bench_time({
rep_scores <- 
  test |> 
  group_by(i) |> 
  group_map(~ scores(.x$N, dat)) |> 
  bind_rows()
})
```

```{r}
library(patchwork)
ggplot(all_scores) + geom_histogram(aes(crps)) + 
(ggplot(all_scores) + geom_histogram(aes(logs)) )

>>>>

```{r}
data <- read_csv("forecasts/block_rnn_stochastic_10.csv.gz")[-1]
```

@@

score_all <- function(data, groups = NULL) {

true <- data |> filter(true_model)
fcst <- data |> filter(!true_model)

dat <- fcst |>
  select(t = time, i = ensemble, N = value) |> 
 pivot_wider(id_cols = "t", names_from="i", values_from = "N") |> 
  select(-t) |> as.matrix()

test <- true  |>
  select(t = time, i = ensemble, N = value)

rep_scores <- 
  test |> 
  group_by(i) |> 
  group_map(~ scores(.x$N, dat)) |> 
  bind_rows()

bind_cols(rep_scores, groups)
}

rep_scores <- data |> 
  group_by(iter, ml_model, tp_model) |>
  group_map(~ score_all(.x, .y) ,.keep = TRUE) |> 
  bind_rows()
```

```{r}
# crude demo
ggplot(rep_scores) + geom_density(aes(crps, color=iter, group=iter)) + facet_grid(ml_model~tp_model)
